---
title: "Project APP: Predicting your salary"
author: "David Peng"
date: "September 20, 2014"
output: slidy_presentation
---

## Overview
####Main components:
- Input panel
- Verify input infos
- Output

####Algorithm
- Wage data set in ISLR
- multivariable linea regression model
- prediction

## Input panel
####Items to input 
- all with default values
- Your wage, text input
- Your Age, a slide bar
- Your education, a select bar (5 categories)
- Your jobclass, a select bar (2 categories)

## Output panel
####Item to verify 
- shows input wage/default
- shows input age/default
- shows input education/default
- shows input jobclass/default
- reactive variables, update in real time

####Items to output
- all controled by buttons
- predicted value and percentile
- message based on the input/predict wages
- histogram shows your percentile

## Algorithm
```{r, echo=FALSE}
data<-matrix(c(rep(1,1000),rgamma(n = 1000, shape = 13.5, rate = .32),
                   sample(c(rep(1,89), rep(2,324), rep(3,217), rep(4,228), rep(5,142))),
                   sample(c(rep(1,515), rep(2, 485)))), nrow=1000, ncol=4)
coef<-c(43.08, .5554, 12,4.5)
data<-data%*%coef
```
- Wage data set in ISLR
- multivariable linea regression model
- prediction

```{r, echo=FALSE}
hist(data, xlab = "Annual Salary", main="Histogram of Salaries", col = "lightgreen", breaks = 20)
lines(x=c(100,100), y=c(0,500), col = "red", lwd=5)
lines(x=c(90,90), y=c(0,500), col = "blue", lwd=5)
legend("topright", legend=c("predicted salary", "input salary"), col = c("red", "blue"), lty = 1, bty="n", lwd = 5)
```